Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-29 manuscript/manuscript.Rmd
Move JSON stuff to supplement

We developed an application that runs completely on the user's local web browser. This simplifies the infrastructure challenge of needing to serve many crowdsdourced workers simultaneously. The web application is configured with a simple JavaScript Object Notation (JSON) file that describes the landmarks necessary to complete an image digitization task. Below is an example JSON file that demonstrates the utility of our web app:

Each digitization task to be completed is given a short abbreviation to aid task identification ("C" for center, "D" for diameter, and "O" for outline), and the type of task, "point", "line" or "curve", for homologous landmarks, linear measurements, and sliding semilandmarks can be specified. There is also an optional short help snippet displayed inline, which serve as a brief reminder for each landmark and complements a larger and more detailed protocol document that workers are required to read before beginning work (Supplementary Material).

@@

XXX: Best practices for turking

>>>>

We developed an application that runs completely on the user's local web browser. This simplifies the infrastructure challenge of needing to serve many crowdsdourced workers simultaneously. The web application is configured with a simple JavaScript Object Notation (JSON) file that describes the landmarks necessary to complete an image digitization task (for more details, see Supplementary Material).

@@

Below is an example JSON file that demonstrates the utility of our web app:

Each digitization task to be completed is given a short abbreviation to aid task identification ("C" for center, "D" for diameter, and "O" for outline), and the type of task, "point", "line" or "curve", for homologous landmarks, linear measurements, and sliding semilandmarks can be specified. There is also an optional short help snippet displayed inline, which serve as a brief reminder for each landmark and complements a larger and more detailed protocol document that workers are required to read before beginning work.
